Comparing Models of Delta-Notch Signalling

### 2025-04-12 paper/paper.tex

\subsection*{Key Assumptions}

Throughout this derivation, we make the following assumptions:

\begin{enumerate}
  \item The standard deviation of the molecular counts is small compared to their mean values. Specifically:
  \begin{itemize}
    \item $\sqrt{\text{Var}(N)} \ll \langle n \rangle$
    \item $\sqrt{\text{Var}(D)} \ll \langle d \rangle$
    \item $\sqrt{\text{Var}(I)} \ll \langle i \rangle$
  \end{itemize}

  \item As a consequence of assumption 1, we can approximate:
  \begin{itemize}
    \item $\langle n^2 \rangle \approx \langle n \rangle^2$
    \item $\langle d^2 \rangle \approx \langle d \rangle^2$
    \item $\langle i^2 \rangle \approx \langle i \rangle^2$
  \end{itemize}

  \item The molecular counts are approximately independent, allowing us to factorize expected values:
  \begin{itemize}
    \item $\langle n \cdot d \rangle \approx \langle n \rangle \cdot \langle d \rangle$
    \item $\langle n \cdot i \rangle \approx \langle n \rangle \cdot \langle i \rangle$
    \item $\langle d \cdot i \rangle \approx \langle d \rangle \cdot \langle i \rangle$
  \end{itemize}

  \item For functions $H^+$ and $H^-$, we approximate:
  \begin{itemize}
    \item $\langle H^+(i) \rangle \approx H^+(\langle i \rangle)$
    \item $\langle H^-(i) \rangle \approx H^-(\langle i \rangle)$
    \item $\langle n \cdot H^+(i) \rangle \approx \langle n \rangle \cdot H^+(\langle i \rangle)$
    \item $\langle d \cdot H^-(i) \rangle \approx \langle d \rangle \cdot H^-(\langle i \rangle)$
  \end{itemize}
\end{enumerate}

>>>>

\subsection*{Key Assumptions}
Throughout this derivation, we make the following assumptions:
\begin{enumerate}
  \item The standard deviation of molecular counts is small compared to their mean values, $\sqrt{\text{Var}(N)} \ll \langle n \rangle$, $\sqrt{\text{Var}(D)} \ll \langle d \rangle$, and $\sqrt{\text{Var}(I)} \ll \langle i \rangle$.

  \item The second moments can be approximated by the squares of the means, i.e., $\langle n^2 \rangle \approx \langle n \rangle^2$, $\langle d^2 \rangle \approx \langle d \rangle^2$, and $\langle i^2 \rangle \approx \langle i \rangle^2$.

  \item Molecular counts are approximately independent, so that joint moments factorize, e.g., $\langle n \cdot d \rangle \approx \langle n \rangle \langle d \rangle$.

  \item For Hill functions $H^+$ and $H^-$, we approximate expectation values by evaluating the function at the mean, i.e., $\langle H(i) \rangle \approx H(\langle i \rangle)$, and similarly $\langle x \cdot H(i) \rangle \approx \langle x \rangle H(\langle i \rangle)$.
\end{enumerate}
